---
title: "Programming Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 데이터 파일

다음과 같은 세개의 파일을 사용한다.

* outcome-of-care-measures.csv: Contains information about 30-day mortality and readmission rates for heart attacks, heart failure, and pneumonia for over 4,000 hospitals.
* hospital-data.csv: Contains information about each hospital.
* Hospital_Revised_Flatfiles.pdf: Descriptions of the variables in each file (i.e the code book).

## 과제 제출 :세개의 함수 제작

1. Finding the best hospital in a state

```{r,eval=FALSE}
best <- function(state, outcome) {
        ## Read outcome data

        ## Check that state and outcome are valid
        ## Return hospital name in that state with lowest 30-day death rate
        
}
```

2.  Ranking hospitals by outcome in a state

```{r,eval=FALSE}
rankhospital <- function(state, outcome, num = "best") {
        ## Read outcome data

        ## Check that state and outcome are valid
        ## Return hospital name in that state with the given rank
        ## 30-day death rate
}
```

3. Ranking hspitals in all states

```{r,eval=FALSE}
rankall <- function(outcome, num = "best") {
        ## Read outcome data

        ## Check that state and outcome are valid
        ## For each state, find the hospital of the given rank
        ## Return a data frame with the hospital names and the
        ## (abbreviated) state name
}
```


## 과제제출

하나의 R파일에 세개의 함수를 만든다. R파일의 이름은 자신의 이름으로 한다. 예를 들어 문건웅의 경우 `문건웅.R`로 한다. 이 R파일을 2018년 10월 1일까지 문건웅의 이메일 주소로 제출한다. 보낼 주소는 cardiomoon@gmail.com 이다. 



